PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$

### 2015-03-19 qfenv_paper/ApJ submission/qf_environment.tex
More referee report responses

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \Hbp {H$\beta ^\prime$}
\def \lowenvthresh {0.5}
\def \highenvthresh {3.0}
\def \apradius{2.5}
\def \apheight{35}

@@

\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}

@@

them. In other words, in the recent Universe a substantial fraction of the

@@

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                              & all          &$33553$                       & $29864$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
               & all                & $1086$                      & $2879$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
               & all               & $1560$                      & $3577$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
               & all              & $1668$                      & $2964$                          \\ \hline
Total &      & \multicolumn{2}{c}{77151} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population. 
    \bigskip
\end{table*}

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.

@@

    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
and $H_\mathrm{ap}$ are comoving distances. We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Finally, we measure the environment for each galaxy in our galaxy
sample by counting the number of EDP galaxies, $n_{\mathrm{env}}$, with RA,
Dec, and $z$ within our cylindrical aperture centered around
it. $n_{\mathrm{env}}$ accounts for the statistical weights of the EDP
galaxies. 
For our galaxy sample, the expected $n_{\mathrm{env}}$ given the uniform number density in 
each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\mathrm{env}} \rangle = 1.3$. 
Once we obtain environment measurements for all the galaxies
in our galaxy sample, we classify galaxies with $n_{\mathrm{env}} < 0.5$
to be in ``low" environment densities and galaxies with $n_{\mathrm{env}} > 3$
to be in ``high" environment densities. The high environment cutoff was
selected in order to reduce contamination from galaxies in low
environment densities while maintaining sufficient statistics. In
Section \ref{sec:env_qf_evol} we will also explore higher density
cutoffs for $n_{\mathrm{env}}$.

@@

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify galaxies with $n_{\mathrm{env}} < 0.5$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5.pdf, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

\begin{table} 
  \caption{Best Fit Parameters for $f_{\mathrm{Q}}(\mathcal{M}_{*})$ Fit}
  \label{tab:bestfitparam}
  \begin{center}
    \leavevmode
    \begin{tabular}{clcc} \hline \hline              
    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
$0.05 < z< 0.12$ &$n_{\mathrm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
               &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
                              &               &                       &                           \\ \hline   
$0.2 < z <0.4$ & $n_{\mathrm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
               &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
               &               &                       &                           \\ \hline
$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
               &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
               &               &                       &                           \\ \hline
$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
               &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\mathrm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
\end{table}

>>>>

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \Hbp {H$\beta ^\prime$}
\def \lowenvthresh {0.0}
\def \highenvthresh {3.0}
\def \apradius{2.5}
\def \apheight{35}

@@

\title{PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}

@@

them. {\bf In other words}, in the recent Universe a substantial fraction of the

@@

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with {\bf a time dependent dust attenuation curve of \cite{Charlot:2000aa} and }other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\mathrm{env}} = \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                              & all          &$33553$                       & $29864$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\mathrm{env}} = \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
               & all                & $1086$                      & $2879$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\mathrm{env}} = \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
               & all               & $1560$                      & $3577$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\mathrm{env}} = \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
               & all              & $1668$                      & $2964$                          \\ \hline
Total &      & \multicolumn{2}{c}{77151} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population. 
    \bigskip
\end{table*}

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. {\bf For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.}

@@

    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. {\bf Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
{\bf We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
and $H_\mathrm{ap}$ are comoving distances.} We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Finally, we measure the environment for each galaxy in our galaxy
sample by counting the number of EDP galaxies, $n_{\mathrm{env}}$, with RA,
Dec, and $z$ within our cylindrical aperture centered around
it. $n_{\mathrm{env}}$ accounts for the statistical weights of the EDP
galaxies. 
For our galaxy sample, the expected $n_{\mathrm{env}}$ given the uniform number density in 
each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\mathrm{env}} \rangle = 1.3$. 
Once we obtain environment measurements for all the galaxies
in our galaxy sample, {\bf we classify galaxies with $n_{\mathrm{env}} = 0.0$
to be in ``low" environment densities} and galaxies with $n_{\mathrm{env}} > 3$
to be in ``high" environment densities. The high environment cutoff was
selected in order to reduce contamination from galaxies in low
environment densities while maintaining sufficient statistics. In
Section \ref{sec:env_qf_evol} we will also explore higher density
cutoffs for $n_{\mathrm{env}}$.

@@

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify {\bf galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
{\bf classified as low environment when $n_{\mathrm{env}} = 0.0$ and }as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5.pdf, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. {\bf For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low }and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

\begin{table} 
  \caption{Best Fit Parameters for $f_{\mathrm{Q}}(\mathcal{M}_{*})$ Fit}
  \label{tab:bestfitparam}
  \begin{center}
    \leavevmode
    \begin{tabular}{clcc} \hline \hline              
    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
$0.05 < z< 0.12$ &$n_{\mathrm{env}} = \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
               &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
                              &               &                       &                           \\ \hline   
$0.2 < z <0.4$ & $n_{\mathrm{env}} = \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
               &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
               &               &                       &                           \\ \hline
$0.4 < z < 0.6$      &$n_{\mathrm{env}} = \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
               &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
               &               &                       &                           \\ \hline
$0.6 < z < 0.8$      &$n_{\mathrm{env}} = \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
               &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\mathrm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
\end{table}
